The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-11 rational.tex
small fixes

Given {{c : b1 <-> b2}}

\begin{center}
  \includegraphics{diagrams/neg_lift.pdf}
\end{center}

@@

%% <<<<<<< local
This can be understood in terms of the \emph{logic programming} as
follows. Operator {{eta* : 1 <-> (1/b)*b}} acts as the site of
creation of a new typed logic variable and constructs from it a value
of type {{b}} and its dual of type {{1/b}}. These two values are free
to move independently through the circuit. Operations on one value
affect what operations are possible on the other since they are both
related by an underlying logic variable. Dually, {{eps*}} acts as a
unification site for values of type {{b}} and {{1/b}} flowing along
both branches. If the values are not unifiable duals, then the
specific program sequence fails. Like with logic programming, one can
has many worlds where some might fail, while others make
progress. Sec. \ref{sec:rat} has more details.  If the values are
exactly duals, then unification succeeds and {{eta*}} returns {{1}}.

@@

\item 
\emph{ {{eps_{fst} }} }

{{(-b1)*b2 + b1*b2 <-> 0}}

\begin{center}
  \includegraphics{diagrams/eps_fst.pdf}
\end{center}

@@

\begin{center}
  \includegraphics{diagrams/mult_neg.pdf}
\end{center}

The following isomorphism can be constructed similarly

>>>>

\begin{multicols}{2}
\begin{center}
  \includegraphics{diagrams/neg_lift.pdf}
\end{center}

%subcode{proof} include main
%@ c : b1 <-> b2
%@@ neg c : (-b1) <-> (-b2)
\end{multicols}

@@

%% <<<<<<< local
In terms of \emph{logic programming}, {{eta* : 1 <-> (1/b)*b}} acts as
the site of creation of a new typed logic variable and constructs two
values using it: a value of type {{b}} and its dual of type
{{1/b}}. These two values are free to move independently through the
computation. Operations on one value affect what operations are possible
on the other since they are both related by an underlying logic
variable. The operator {{eps*}} acts as a unification site for values of
type {{b}} and {{1/b}} flowing along both branches. If the values are
not unifiable duals, then the specific program sequence fails. Like
with logic programming, one can has many worlds where some might fail,
while others make progress. Sec. \ref{sec:rat} has more details.  If
the values are exactly duals, then unification succeeds and {{eta*}}
returns {{1}}.

@@

%% \item 
%% \emph{ {{eps_{fst} }} }

%% {{(-b1)*b2 + b1*b2 <-> 0}}

@@

\begin{center}
\scalebox{0.8}{
  \includegraphics{diagrams/eps_fst.pdf}
}
\end{center}

\begin{center}
\scalebox{0.9}{
  \includegraphics{diagrams/mult_neg.pdf}
}
\end{center}

\item
\emph{Multiplying Negatives}
